---
title: "DSC640_Assignment1.2_LincolnBrown"
output: html_notebook
author: Lincoln Brown
class: DSC640-T302
professor: Professor Williams
---

Import the necessary libraries
```{r}
# Install Libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(readxl)
```

Import the data, add it to a dataframe, and display the head
```{r}
hotdog_contest <- read_excel(path="./ex1-2/hotdog-contest-winners.xlsm")
hotdog_contest_df <- data.frame(hotdog_contest)
head(hotdog_contest_df)
```
Bar Graph
This bar graph shows the number of hot dogs eaten by each country. 
```{r}
# Create a Bar graph
# Aggregate data to get the total number of hot dogs eaten per country
agg_data <- hotdog_contest_df %>%
  group_by(Country) %>%
  summarize(total_dogs_eaten = sum(Dogs.eaten))

# Reorder the Country by the total number of hot dogs eaten
agg_data$Country <- reorder(agg_data$Country, agg_data$total_dogs_eaten)

# Create the bar graph with reordered countries
ggplot(agg_data, aes(x = Country, y = total_dogs_eaten)) + 
  geom_bar(stat = "identity", fill = "#698BB2") + 
  labs(title = "Number of Hot Dogs Eaten by Country", x = "Country", y = "Total Number of Hot Dogs Eaten") +
  theme_minimal()
```
Stacked Bar Graph
This stacked bar graph shows the number of hot dogs eaten by each winner, with each year's contribution displayed as a section of the stack. 
```{r}
# Create a Stacked Bar Graph
ggplot(hotdog_contest_df, aes(x = reorder(Winner, Dogs.eaten), y=Dogs.eaten, fill=Year)) +
  geom_bar(stat = "identity") + 
  labs(title = "Hot Dogs Eaten by Winner", x = "Winner", y = "Number of Hot Dogs Eaten") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Pie Chart
This pie chart shows the number of hot dogs eaten by each country. 
```{r}
# Create a pie chart
sum_dogs_eaten <- aggregate(Dogs.eaten ~ Country, data = hotdog_contest_df, FUN = sum)
pie(sum_dogs_eaten$Dogs.eaten, labels = paste(sum_dogs_eaten$Country,sum_dogs_eaten$Dogs.eaten), main = "Total Number of Dogs Eaten by Country", col = brewer.pal(n = nrow(sum_dogs_eaten), name="Blues"))
```
Donut Chart
This donut chart shows the number of records set by each country. Japan and the United States were the only countries that had winners set a new record. 
```{r}
# Create a donut chart
# Aggregate data to get the total number of new records set per country
winner_data <- hotdog_contest_df %>%
  group_by(Country) %>%
  summarize(total_new_records = sum(New.record)) %>%
  filter(total_new_records > 0)

ggplot(winner_data, aes(x = 2, y = total_new_records, fill = Country)) + 
  geom_bar(stat = "identity", width = 1) + 
  coord_polar(theta = "y") +
  theme_void() +
  xlim(0.5, 2.5) +  # Adjust to create the hole in the center
  labs(title = "Total Number of New Records Set by Country") +
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Blues")
```
Line Graph
This line graph shows the total number of hot dogs consumed by the winner each year. 
```{r}
# Create a line graph
ggplot(hotdog_contest_df, aes(x = Year, y = Dogs.eaten))+
          geom_line(color="#698BB2") +
          labs(title = "Number of Hot Dogs Eaten by Year",
               x = "Year", y = "Dogs Eaten") + 
          theme_minimal()
```
